The impact of cosmic variance on simulating weak lensing surveys

### 2014-09-24 Writeup/paper_v3.tex
Figures look better

\begin{figure}
 %\centering
 a) \includegraphics[width=1.1\columnwidth]{rms_ellip1.eps} \
 b) \includegraphics[width=1.1\columnwidth]{rms_ellip2_noevolution.eps} \\
 \caption{Left: RMS ellipticities with ellipticity defined as $\frac{1-q}{1+q}$. \; 
          Right: RMS ellipticities with ellipticity defined as $\frac{1-q^2}{1+q^2}$.\\ The horizontal errorbars simply correspond to the binwidth while the vertical ones
          are $1\sigma$ errorbars obtained by bootstrapping.}
 \label{fig:rms_ellip}
\end{figure}

\begin{figure}
 %\centering
 a) \includegraphics[width=1.1\columnwidth]{rms_ellip1_Bbandevolution_masscut.eps} \
 b) \includegraphics[width=1.1\columnwidth]{rms_ellip2_Bbandevolution_masscut.eps} \\
 \caption{Left: RMS ellipticities with ellipticity defined as $\frac{1-q}{1+q}$. \; 
          Right: RMS ellipticities with ellipticity defined as $\frac{1-q^2}{1+q^2}$.\\ The horizontal errorbars simply correspond to the binwidth while the vertical ones
          are $1\sigma$ errorbars obtained by bootstrapping. The solid points correspond to the sample where the luminosity cut evolves by -1.23 per unit redshift (\s$2$) and the unfilled
          points correspond to the sample obtained from stellar mass cuts (\s$3$).}
 \label{fig:rms_ellip_Bband_mass}
\end{figure}

@@

When the B-band luminosity evolution is taken into account in selecting the sample, a systematic increase in the ellipticity at lower redshifts can be observed. We plot these alongside with stellar-mass selected samples, where a similar trend is found, in Fig.~\ref{fig:rms_ellip_Bband_mass}. 
Such a trend is not observed in axis ratios based on second moments. 
For other morphological parameters, we do not the distributions themselves directly. For \sersic profile fits, it gets tricky since we truncate the \sersic index at 6. 
For \btt ratios, we force the value to be greater than 0.05 \arun{What exactly do we do here?}. We will understand the dependence of these quantities on environment by computing the median values in different redshift bins.
We choose median over mean since it is more robust to the truncation effects.
Figure(s) \ref{fig:median_sersicn} show the median of the \sersic index with and without taking into account of the luminosity evolution. Median values obtained using stellar mass selected samples are plotted alongside for reference.
We observe that the overdense regions tend to have higher \sersic index than the adjacent underdense ones.
Figure(s) \ref{fig:median_dvcbtt} show the variation of median \btt ratio with redshift. We see that the bulge component is more in overdense regions than in the underdense regions.
These two observations are consistent with each other since higher \sersic index implies higher bulge component which are typical in young galaxies found in overdense regions.
%We chose median over mean since \sersic n greater than 6 are truncated to 6. This affects the mean statistic more than the median.
\begin{figure}
 %\centering
 \includegraphics[width=1.1\columnwidth]{median_sersicn}
 \includegraphics[width=1.1\columnwidth]{median_sersicn(2)}
 \caption{Median values of the \sersic indices for volume-limited samples \s$1$ and \s$3$ are plotted (filled centers and thin errorbars) in left and right panels respectively for each redshift bin.
          Median values for the \s$2$ sample are plotted in both the panels (open centers and thick errorbars) in both the panels.
          The horizontal errorbars simply correspond to the binwidth while the vertical ones are $1\sigma$ errorbars obtained by bootstrapping.}
 \label{fig:median_sersicn}
\end{figure}

\begin{figure}
 %\centering
 \includegraphics[width=1.1\columnwidth]{median_dvcbtt}
 \includegraphics[width=1.1\columnwidth]{median_dvcbtt(2)}
  \caption{Median values of the \btt ratios for volume-limited samples \s$1$ and \s$3$ are plotted (filled centers and thin errorbars) in left and right panels respectively for each redshift bin.
          Median values for the \s$2$ sample are plotted in both the panels (open centers and thick errorbars) in both the panels.
          The horizontal errorbars simply correspond to the binwidth while the vertical ones are $1\sigma$ errorbars obtained by bootstrapping.}
 \label{fig:median_dvcbtt}
\end{figure}

>>>>

\begin{figure}
 %\centering
 a) \includegraphics[width=1.0\columnwidth]{rms_ellip1_noevolution.eps} \
 b) \includegraphics[width=1.0\columnwidth]{rms_ellip2_noevolution.eps} \\
 \caption{Left: RMS ellipticities with ellipticity defined as $\frac{1-q}{1+q}$. \; 
          Right: RMS ellipticities with ellipticity defined as $\frac{1-q^2}{1+q^2}$.\\ The horizontal errorbars simply correspond to the binwidth while the vertical ones
          are $1\sigma$ errorbars obtained by bootstrapping.}
 \label{fig:rms_ellip}
\end{figure}

\begin{figure}
 %\centering
 a) \includegraphics[width=1.0\columnwidth]{rms_ellip1_Bbandevolution.eps} \
 b) \includegraphics[width=1.0\columnwidth]{rms_ellip2_Bbandevolution.eps} \\
 \caption{Left: RMS ellipticities with ellipticity defined as $\frac{1-q}{1+q}$. \; 
          Right: RMS ellipticities with ellipticity defined as $\frac{1-q^2}{1+q^2}$.\\ The horizontal errorbars simply correspond to the binwidth while the vertical ones
          are $1\sigma$ errorbars obtained by bootstrapping. The solid points correspond to the sample where the luminosity cut evolves by -1.23 per unit redshift (\s$2$) and the unfilled
          points correspond to the sample obtained from stellar mass cuts (\s$3$).}
 \label{fig:rms_ellip_Bband_mass}
\end{figure}

@@

When the B-band luminosity evolution is taken into account in selecting the sample, a systematic increase in the ellipticity at lower redshifts can be observed. We plot these alongside with stellar-mass selected samples, where a similar trend is found, in Fig.~\ref{fig:rms_ellip_Bband_mass}. 
Such a trend is not observed in axis ratios based on second moments. 
For other morphological parameters, we do not the distributions themselves directly. For \sersic profile fits, it gets tricky since we truncate the \sersic index at 6. 
For \btt ratios, we force the value to be greater than 0.05 \arun{What exactly do we do here?}. We will understand the dependence of these quantities on environment by computing the median values in different redshift bins.
We choose median over mean since it is more robust to the truncation effects.
Figure(s) \ref{fig:median_sersicn} show the median of the \sersic index with and without taking into account of the luminosity evolution. Median values obtained using stellar mass selected samples are plotted alongside for reference.
We observe that the overdense regions tend to have higher \sersic index than the adjacent underdense ones.
Figure(s) \ref{fig:median_dvcbtt} show the variation of median \btt ratio with redshift. We see that the bulge component is more in overdense regions than in the underdense regions.
These two observations are consistent with each other since higher \sersic index implies higher bulge component which are typical in young galaxies found in overdense regions.
%We chose median over mean since \sersic n greater than 6 are truncated to 6. This affects the mean statistic more than the median.
\begin{figure}
 %\centering
 \includegraphics[width=1.1\columnwidth]{median_sersicn}
 \includegraphics[width=1.1\columnwidth]{median_sersicn2}
 \caption{Median values of the \sersic indices for volume-limited samples \s$1$ and \s$3$ are plotted (filled centers and thin errorbars) in left and right panels respectively for each redshift bin.
          Median values for the \s$2$ sample are plotted in both the panels (open centers and thick errorbars) in both the panels.
          The horizontal errorbars simply correspond to the binwidth while the vertical ones are $1\sigma$ errorbars obtained by bootstrapping.}
 \label{fig:median_sersicn}
\end{figure}

\begin{figure}
 %\centering
 \includegraphics[width=1.1\columnwidth]{median_dvcbtt1}
 \includegraphics[width=1.1\columnwidth]{median_dvcbtt2}
  \caption{Median values of the \btt ratios for volume-limited samples \s$1$ and \s$3$ are plotted (filled centers and thin errorbars) in left and right panels respectively for each redshift bin.
          Median values for the \s$2$ sample are plotted in both the panels (open centers and thick errorbars) in both the panels.
          The horizontal errorbars simply correspond to the binwidth while the vertical ones are $1\sigma$ errorbars obtained by bootstrapping.}
 \label{fig:median_dvcbtt}
\end{figure}
